The Calculus of Linear Constructions

### 2021-10-12 writing/draft1.tex
draft

  However, due to its origins as a logical framework for constructive mathematics, it is quite difficult for CC to encode and reason about resources. Intuitively, a mathematical theorem can be applied an unrestricted number of times. Comparatively, the usage of resources is more limited. For example, if we encode Girard's classical example \cite{girard95} of purchasing cigarettes literally into CC as a function of type:
  \begin{equation*}
    Money \rightarrow Camels + Marlboro
  \end{equation*}
  If viewed as an propositional implication, the customer will still maintain full ownership of their money after paying the vendor, because implication does not diminish the validity of its antecedent. Unless the vendor is exceedingly generous, we are faced with the crime of counterfeiting. Users of proof assistants based on CC often need to embed external logics \cite{bedrock} to provide additional reasoning principles for dealing with resource. The design and embedding of these logics is a difficult problem in its own right, requiring additional proofs to justify its soundness. We propose an alternative solution: extend CC with linear types.

>>>>

  However, due to its origins as a logical framework for constructive mathematics, it is quite difficult for CC to encode and reason about resources. Intuitively, a mathematical theorem can be applied an unrestricted number of times. Comparatively, the usage of resources is more limited. For example, if we encode Girard's classical example \cite{girard95} of purchasing cigarettes literally into CC as a function of type:
  \begin{equation*}
    Money \rightarrow Camels + Marlboro
  \end{equation*}
  If viewed as a propositional implication, the customer will still maintain full ownership of their money after paying the vendor, because implication does not diminish the validity of its antecedent. Unless the vendor is exceedingly generous, we are faced with the crime of counterfeiting. Users of proof assistants based on CC often need to embed external logics \cite{bedrock} to provide additional reasoning principles for dealing with resource. The design and embedding of these logics is a difficult problem in its own right, requiring additional proofs to justify its soundness. We propose an alternative solution: extend CC with linear types.
